Order reduction and MILP models for real-time DNN robustness certification.

### 2025-11-10 CAV 2026/introduction.tex
update

	\item We develop a novel exact MILP encoding for the global robustness problem,
	called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}). We study and encode exactly in MILP how the {\em diff variables} evolve after passing through a ReLU (Prop.~\ref{Prop2}). Compared with the
	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz, ITNE},
	the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other. This was observed in \cite{lipshitz, ITNE}, and constraints encoding
	a part of the linear relaxation of our "2v" model were added explicitly. Experimentally, 
	our "2v" model provides more accurate bounds than competing models, in the same runtime
	(Table \ref{table.classical}).
	%The number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed. 
	%Recall that the worst case complexity of MILP is exponential in the number of binary variables \cite{DivideAndSlide}. 
	%A straightforward MILP model would be to use the  for each of these variables, as in \cite{vhagar,lipshitz}. The main issue with the classical model is that its linear relaxations is extremely inaccurate, as the variables are independent of each other. Instead, we develop another exact MILP model, 
	Further, we develop two abstract MILP models, namely the "3v" model which decouples the 
	{\em non-diff binary variables} of the "2v" model, resulting in looser bounds but with lower runtimes, as well as a computationally efficient "1v" model that only considers the 
	{\em diff variables}, however resulting in much looser bounds.
	%\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation. The chosen number of binary variables depends upon the complexity of the DNN as well as the targeted runtime.

>>>>

	\item We develop a novel exact MILP encoding for the global robustness problem,
	called the {\em "2v" model}, where the variables are the values of the perturbed neurons, as well as the difference between the original and the perturbed neuron values (called the {\em diff variables}). We study and encode exactly in MILP how the {\em diff variables} evolve after passing through a ReLU (Prop.~\ref{Prop2}). Compared with the
	{\em classical MILP model} \cite{MILP} employed in \cite{vhagar,lipshitz,ITNE},
	the linear relaxation is much more accurate, as each {\em diff variable} can be bounded after a ReLU as a function of the value of the {\em diff variables} before the ReLU, whereas the linear relaxations of the classical model is extremely inaccurate, as the variables are independent of each other. This was observed in \cite{lipshitz,ITNE}, and constraints encoding
	a part of the linear relaxation of our "2v" model were added explicitly. Experimentally, 
	our "2v" model provides more accurate bounds than competing models, in the same runtime
	(Table \ref{table.classical}).
	%The number of variables a priori doubles compared with local robustness, from each neuron value in the perturbed image to each neuron value in the perturbed image {\em and} in the original image, as the original image is no more fixed. 
	%Recall that the worst case complexity of MILP is exponential in the number of binary variables \cite{DivideAndSlide}. 
	%A straightforward MILP model would be to use the  for each of these variables, as in \cite{vhagar,lipshitz}. The main issue with the classical model is that its linear relaxations is extremely inaccurate, as the variables are independent of each other. Instead, we develop another exact MILP model, 
	Further, we develop two abstract MILP models, namely the "3v" model which decouples the 
	{\em non-diff binary variables} of the "2v" model, resulting in looser bounds but with lower runtimes, as well as a computationally efficient "1v" model that only considers the 
	{\em diff variables}, however resulting in much looser bounds.
	%\item We adapt the Solution Aware Scoring from \cite{ATVA25} to our novel MILP models, in order to select the most important ReLUs to be treated using complex binary variables, while less important variables are treated using linear relaxation. The chosen number of binary variables depends upon the complexity of the DNN as well as the targeted runtime.

### 2025-11-10 CAV 2026/notation.tex
update

    In this paper, we consider the {\em global} verification problem, where we optimize over all images $I$ and perturbations $I'$ of $I$ with $|I-I'| \leq \varepsilon$. We will consider three kinds of variables: 
    \begin{itemize}
    \item $x_j,\hat{x}_j$, for nodes $j$ with input image $I$, 
    \item $x'_j,\hat{x}'_j$, for nodes $j$ with input the perturbed $I'$, 
    \item  $y_j = x_j - x'_j$ the {\em diff variable}, with 
    $\hat{y}_j = \hat{x}_j - \hat{x}'_j$ (and {\em not} 
    $\hat{y}_i = \ReLU(x_j-x'_j)$), similarly than in the 
	Interleaving Twin-Network Encoding (ITNE) model of \cite{lipshitz, ITNE}. 
    \end{itemize}

>>>>

    In this paper, we consider the {\em global} verification problem, where we optimize over all images $I$ and perturbations $I'$ of $I$ with $|I-I'| \leq \varepsilon$. We will consider three kinds of variables: 
    \begin{itemize}
    \item $x_j,\hat{x}_j$, for nodes $j$ with input image $I$, 
    \item $x'_j,\hat{x}'_j$, for nodes $j$ with input the perturbed $I'$, 
    \item  $y_j = x_j - x'_j$ the {\em diff variable}, with 
    $\hat{y}_j = \hat{x}_j - \hat{x}'_j$ (and {\em not} 
    $\hat{y}_i = \ReLU(x_j-x'_j)$), similarly than in the 
	Interleaving Twin-Network Encoding (ITNE) model of \cite{lipshitz,ITNE}. 
    \end{itemize}
